### 2014-05-19 ApTranscriptome_TR.Rmd
working on partitioning true 'Low' from 'Off high'

## Species comparison ##

@@

# list of transcripts that are 'Intermediate' expressed in A22
A22.int.transcripts <- Ap.response.type[which(Ap.response.type$A22.type == "Intermediate"), ]
# T test
t.test(log(A22.int.transcripts$A22.opt+1), log(A22.int.transcripts$Ar.opt+1))
# Wilcoxon signed rank-test
wilcox.test(A22.int.transcripts$A22.opt, A22.int.transcripts$Ar.opt, alternative = "two.sided", paired = TRUE, conf.int = TRUE)
```

@@

@@

```{r rData, echo=FALSE}
# save RData for manuscript file
save(RxNpval, sigtable, chi1, resp.TPM.dt.sub, tt2, tt3, GO.stress.Xsq, GO0006950.responsive, Ap.df, w1, w2, Ap.T_on, Ap.BP.resultParentChild, Ap.gsea1, Ap.setdiff.gsea, resp.stress.responsive.count, t.mean, t.slope, t.curvature, t.wiggle, t.themsens, t.thermbreadth, file = "ms.RData")
```

>>>>

## Species comparison

@@

# list of transcripts that are 'Intermediate' expressed in A22
A22.int.transcripts <- Ap.response.type[which(Ap.response.type$A22.type == "Intermediate"), ]
# T test
t.test(log(A22.int.transcripts$A22.opt+1), log(A22.int.transcripts$Ar.opt+1))
# Wilcoxon signed rank-test
wilcox.test(A22.int.transcripts$A22.opt, A22.int.transcripts$Ar.opt, alternative = "two.sided", paired = TRUE, conf.int = TRUE)

# list of transcripts that are 'Intermediate' expressed in either colony
Ap.int.transcripts <- Ap.response.type[which(Ap.response.type$Ar.type == "Intermediate" | Ap.response.type$A22.type == "Intermediate"), ]
# T test
t.test(log(Ap.int.transcripts$A22.opt+1), log(Ap.int.transcripts$Ar.opt+1))
# Wilcoxon signed rank-test
w3 <- wilcox.test(Ap.int.transcripts$A22.opt, Ap.int.transcripts$Ar.opt, alternative = "two.sided", paired = TRUE, conf.int = TRUE)
w3
```

@@

### Overlap between *Ar* Intermediate and *A22* Low genes

```{r gene_overlap}
# transcripts that are low in A22 and intermediate in Ar
A22.low.Ar.int <- Ap.response.type[which(Ap.response.type$A22.type == "Low" & Ap.response.type$Ar.type == "Intermediate"), "Transcript"]
A22.low.Ar.int.lms <- responsive.lms[A22.low.Ar.int]

# transcripts that are low in both A22 and Ar
A22.low.Ar.low <- Ap.response.type[which(Ap.response.type$A22.type == "Low" & Ap.response.type$Ar.type == "Low"), "Transcript"]
A22.low.Ar.low.lms <- responsive.lms[A22.low.Ar.low]

head(int.low.overlap)

# compare linear and quadratic model terms

# transcripts where TPM increases at low temps & decreases at high temps
A22.low.Ar.int.TPM.dt.sub <- resp.TPM.dt.sub.pred[J(intersect(A22.low,Ar.int), "A22")]

for(i in unique(A22.low.Ar.int.TPM.dt.sub$Transcript)[1:10]) {
    s <- A22.low.Ar.int.TPM.dt.sub[i]
    X11()
    plot(s$val, s$pTPM, ylim = c(0, max(s$pTPM)+.1))
    points(s$val, s$TPM, pch = 8, col = "red")
    if(min(s[which(s$val < 30) , pTPM]) < s[which(s$val == 38.5), pTPM]) print("On low") else {
        print("Off high")
    }
}

# A22 low Ar int
A22.low.Ar.int.low.type <- ddply(A22.low.Ar.int.TPM.dt.sub, .(Transcript), summarise, lt = ifelse(pTPM[which(val == 38.5)] == min(pTPM), "OffHigh", "OnLow"))

table(A22.low.Ar.int.low.type$lt)

# A22 low Ar low
A22.low.Ar.low.TPM.dt.sub <- resp.TPM.dt.sub.pred[J(intersect(A22.low, Ar.low), "A22")]

# transcripts where TPM increases at low temps & decreases at high temps

A22.low.Ar.int.TPM.dt.sub <- resp.TPM.dt.sub.pred[J(intersect(A22.low, Ar.int), "A22")]
dim(A22.low.Ar.int.TPM.dt.sub)

l5 <- length(unique(A22.low.Ar.int.TPM.dt.sub$Transcript))

A22.low.Ar.int.T_on <- data.frame(Transcript = unique(A22.low.Ar.int.TPM.dt.sub$Transcript), colony = rep("ApVT", length = l5), type = rep("High", length = l5), T_on = NA)

# of these, how many have greatest change in expression as a decrease at high temperatures?
for(i in unique(A22.low.Ar.int.TPM.dt.sub$Transcript)) {
    subdf <- A22.low.Ar.int.TPM.dt.sub[i]
    T_on <- subdf[median(which(diff(subdf$TPM) == max(diff(subdf$TPM))))+1, val]
    A22.low.Ar.int.T_on[which(A22.low.Ar.int.T_on$Transcript == i), "T_on"] <- T_on
}

@@

```{r rData, echo=FALSE}
# save RData for manuscript file
save(RxNpval, sigtable, chi1, resp.TPM.dt.sub, tt2, tt3, GO.stress.Xsq, GO0006950.responsive, Ap.df, w1, w2, w3, Ap.T_on, Ap.BP.resultParentChild, Ap.gsea1, Ap.setdiff.gsea, resp.stress.responsive.count, t.mean, t.slope, t.curvature, t.wiggle, t.themsens, t.thermbreadth, file = "ms.RData")
```
